\vspace{-1.5cm} STA610 Case Study 1 Team 4 Report

### 2021-03-22 final 3.Rmd
Added FINAL writeup

---
title: STA610 Case Study 1 Team 4 Report
author:
- Cole Juracek (Programmer)
- Lauren Palazzo (Writer)
- Lingyu Zhou (Checker + Coordinator)
- Fan Zhu (Presenter)
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
fontsize: 11pt
geometry: margin=1.5cm
---

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(pacman)
library(merTools)
pacman::p_load(tidyverse, lme4, gridExtra, grid, ggplot2, lattice, redres, stringr,
               influence.ME, knitr)
# devtools::install_github("goodekat/redres")
```

@@

We performed an initial examination of two grouping variables, `state` and `USA_region`. The state North Dakota had only one observation, and as such was not considered a well-defined "group" for which a variance could be estimated; thus this state's observation was removed. States labeled simply as "USA" were recoded to "Unknown". Region was also sometimes labeled as uknown or other; these observations coincided with the unknown states (see appendix Table X). (The variable `city` as a grouping variable is addressed later in the report.)

@@

```{r, echo = FALSE}
# Change date to numeric (easier for interpretation)
# this sets 
df$date_num <- as.numeric(as.Date(df$price_date, "%m/%d/%y")) - 14621 # sets 1/12/2010 (first post-2010 date) as zero
tempdf <- df %>% select(date_num, price_date)
# this filters out all data before the 1/1/2000, which probably shouldn't be included
df <- df %>% filter(date_num >= 0)
```

@@

```{r, fig.align='center', fig.height=4}
plotREsim(REsim(mod_final,n.sims=100),stat='median',sd=TRUE, labs = TRUE)
```
From the result of the random effects, we can see that the random intercept for Tennessee is the highest and it is significantly different from zero. The random intercept for Arizona is the lowest and this intercept is also significant.

@@

## Code

```{r, ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}

```

@@

hist(group_int_list)
hist(group_slope_list)

@@

hist(group_int_list)
hist(group_slope_list)
```

>>>>

---
title: \vspace{-1.5cm} STA610 Case Study 1 Team 4 Report
author:
- Cole Juracek (Programmer)
- Lauren Palazzo (Writer)
- Lingyu Zhou (Checker + Coordinator)
- Fan Zhu (Presenter)
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
fontsize: 11pt
geometry: margin=1.5cm
---

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(pacman)
devtools::install_github("goodekat/redres")
pacman::p_load(tidyverse, lme4, gridExtra, grid, ggplot2, lattice, redres, stringr,
               influence.ME, knitr, merTools)
```

@@

We performed an initial examination of two grouping variables, `state` and `USA_region`. The state North Dakota had only one observation, and as such was not considered a well-defined "group" for which a variance could be estimated; thus this state's observation was removed. States labeled simply as "USA" were recoded to "Unknown". Region was also sometimes labeled as uknown or other; these observations coincided with the unknown states. (The variable `city` as a grouping variable is addressed later in the report.)

@@

```{r, echo = FALSE}
# Change date to numeric (easier for interpretation)
# this sets 
df$date_num <- as.numeric(as.Date(df$price_date, "%m/%d/%y")) - 14621 # sets 1/12/2010 (first post-2010 date) as zero
tempdf <- df %>% dplyr::select(date_num, price_date)
# this filters out all data before the 1/1/2000, which probably shouldn't be included
df <- df %>% filter(date_num >= 0)
```

@@

```{r, fig.align='center', fig.height=6, fig.width=8}
plotREsim(REsim(mod_final,n.sims=100),stat='median',sd=TRUE, labs = TRUE)
```

The value of the random intecepts range from exp(0.450007131) = 1.568323 for Tenessee to exp(-0.417349014) = 0.658791 for Nevada. We interpret this as follows: the estimated average value for ppm of oxymorphone is highest for Tennessee. The price is estimated assuming a non-bulk purchase, unknown source, blank reason, and zero dose per mg (which is obviously not a realistic value, but is noted for the sake of interpretation).

@@

@@

par(mfrows=c(2, 1))
hist(group_int_list)
hist(group_slope_list)

@@

par(mfrows=c(2, 1))
hist(group_int_list)
hist(group_slope_list)
```
